The pooling of keypoint descriptors aims to reduce dimensionality and achieve invariance to transformations by aggregating features or descriptors over regions of an image as done with the SIFT descriptor in Dong, Jingming and Soatto, Stefano's work on DSP-SIFT\cite{dong2015domain}. This research seeks to investigate this method by implementing, optimizing, and bench-marking a variety of both experimental and established descriptors under different pooling configurations. Through this focus on pooling, the study endeavors to explore how aggregating the attributes of individual keypoints into pooled descriptors can lead to a more robust and efficient descriptor representation, with the potential to enhance the accuracy and reliability of computer vision tasks. 

The principle focus of this research is primarily aimed at exploring the optimal pooling of descriptors, as opposed to or in combination with stacking, to improve computer vision applications. Initially, this study endeavors to implement a varied range of descriptor pooling strategies, drawing insights from both classical and contemporary studies. Secondly, it aims to augment the efficacy of these pooled descriptors through careful optimization processes used for keypoint descriptor construction and matching, although the emphasis on leveraging advancements in GPU and tensor cores will be relegated to a potential stretch goal. Lastly, a bench-marking exercise is planned to evaluate the performance of these pooled descriptors, with a particular focus on both precision and recall, essential metrics for understanding the accuracy and completeness of the descriptor matching process.

By investigating the performance outcomes of descriptor pooling, this study aims to contribute empirical evidence to the broader field of computer science. The anticipated findings are intended to enhance practical methodologies and applications in computer vision.

Subsequent sections of this proposal will speak to the research background underscoring the importance of this study, a comprehensive methodology encapsulating the implementation, optimization, and bench-marking processes, and the projected implications of the anticipated discoveries.